Generating the Blueprints of the Java Ecosystem

### 2015-02-27 msr.tex
Refactor Ch1 and Ch2

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{c}
   \affaddr{\aueb Dept of Management Science and Technology}\\
   \affaddr{Athens University of Economics and Business}\\
   \affaddr{Athens, Greece}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
  \end{tabular}
  \centering
  \begin{tabular}{cc}
   \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}

@@

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Software development artifacts consist of digital data, thus many of their aspects can be easily measured. This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code). Over the years, a wealth of different metrics have appeared in the literature. Many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.

In this paper, we present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java. All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}. Maven is a build automation tool used mostly for Java projects. To build a software component, it dynamically downloads Java libraries and Maven plug-ins from the Maven central repository, and stores them in a local cache. The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions. To analyze the projects coming from this repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}. All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design.

@@

Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}. The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala. All languages use the {\sc jvm} platform as their runtime environment.

@@

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects that contain several versions. In our experiment, we only used Java projects. For every Java project all versions were filtered out and only the latest was kept.

@@

When the selection process was finished, we created a series of processing tasks based on the containing all the selected {\sc jar}s, and added them to a task queue mechanism.  Then we executed a number of workers
% dimitro@bkarak: written in?
that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system). The tools that were applied on every {\sc jar} were the following.

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.

@@

% A series of secondary metrics wesre also stored in the database. For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project. These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted. dimitro@bkarak: then why do you mention it?

In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset anf therefore for the Java ecosystem in general.

>>>>

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{c}
   \affaddr{\aueb Dept of Management Science and Technology}\\
   \affaddr{Athens University of Economics and Business}\\
   \affaddr{Athens, Greece}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
  \end{tabular}
  \centering
  \begin{tabular}{cc}
   \affaddr{} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{g.gousios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}

@@

% gousiosg: This is MSR -> no need of stating the obvious
% gousiosg: if you want, write a paragraph saying that science needs badly a dataset like the one you offer

%Software metrics provide a means to extract useful and measurable information about the structure of a software system. Software development artifacts consist of digital data, thus many of their aspects can be easily measured. This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code). Over the years, a wealth of different metrics have appeared in the literature. Many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.

We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java. All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}. The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala. All supported languages use the {\sc jvm} platform as their runtime environment.
To build a software component, it dynamically downloads Java libraries and Maven plug-ins from the Maven central repository, and stores them in a local cache. The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.

To analyze the projects coming from Maven repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}. All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design.

@@

@@

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects that contain several versions. In our experiment, we only used Java projects. For every Java project
%gousiosg: say how you identified java projects. Previous datasets failed to
% do this, therefore it is a strong point
all versions were filtered out and only the latest was kept.

@@

When the selection process was finished, we created a series of processing tasks based on the containing all the selected {\sc jar}s, and added them to a task queue mechanism.  Then we executed a number of workers
% dimitro@bkarak: written in?
% gousiosg: ref dimitro's paper and say you followed the same process
that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system). The tools that were applied on every {\sc jar} were the following.

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g}
%is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It
calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in GitHub~\cite{CKJM}.

@@

% A series of secondary metrics wesre also stored in the database. For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project. These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted. 
% dimitro@bkarak: then why do you mention it?
% gousiosg: @dimitro: I agree with your comment. However, identifying the 
% DSLs is a worthy contribution. @bkarak: I would rephrase and add a description of
% how you identified the DSLs. Then also mention this in the research
% opportunities

In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
